Do We Judge Children's Books by Their Covers? 

### 2024-12-03 paper/paper.qmd
Add abstract

---
title: "Do We Judge Children's Books by Their Covers? "
subtitle: "Exploring Title, Exclamation Marks, and Reviewer Bias"
author: 
  - David Qi
thanks: "Code and data are available at: https://https://github.com/UTDQi/children_book_review"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

However, children's books, as a unique genre, present distinct dynamics in the realm of user-generated ratings and recommendation systems. Unlike adult literature, children rarely contribute directly to ratings or reviews. Instead, parents, educators, and caregivers typically provide feedback. Which have made is difficult to create recommendation systems [@judgecover]. And since many reviewer are not direct reader of the book, we hypothysize their rating may subject to greater bias from first impression.

>>>>

---
title: "Do We Judge Children's Books by Their Covers? "
subtitle: "Exploring Title, Exclamation Marks, and Reviewer Bias"
author: 
  - David Qi
thanks: "Code and data are available at: https://https://github.com/UTDQi/children_book_review"
date: today
date-format: long
abstract: "This study examines the impact of first impressions on children's book ratings, focusing on how attributes such title, page count, and review count influence ratings. Using data from Goodreads and both simple linear regression and fine-tuned transformer models, we found that book titles alone explained 7.94% of the variation in ratings, indicating the significance of first impressions. This study provide support for previous studies in concluding that children may favor the theme of excitement and celebration, which are useful in building recommendation system and selecting optimal titles."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

However, children's books, as a unique genre, present distinct dynamics in the realm of user-generated ratings and recommendation systems. Unlike adult literature, children rarely contribute directly to ratings or reviews. Instead, parents, educators, and caregivers typically provide feedback. Which have made is difficult to create recommendation systems [@judgecover]. And since many reviewer are not direct reader of the book, we hypothesize their rating may subject to greater bias from first impression.
